Bioverse: Origins of Life

### 2024-07-08 src/tex/ms.tex
describe star and planet generation

\subsubsection{Habitable zone occupancy and UV flux}
To test the UV hypothesis, we require that life occurs only on planets with sufficient past UV irradiation exceeding $F_\mathrm{NUV, min}$.
Further, we require this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.
All common Origin of Life scenarios require water as a solvent;
we thus consider only rocky planets that may sustain liquid water on their surface, i.e., that occupy their momentary \gls{HZ} during the above period.

Different formulations of habitable zones as regions around a star where a planet with Earth's atmospheric composition can maintain liquid water on its surface exist~\citep[e.g.,][]{MolLous2022,Spinelli2023,Tuchow2023}. CITE! Ramirez \& Kaltenegger 2017, 2018
Here, we adopt the popular estimates of \citet{Kasting1993} and \citet{Kopparapu2013,Kopparapu2014} that define a temperate zone between the runaway greenhouse transition CITE! and the maximum greenhouse limit CITE!.
We use the parametrization in \citet{Kopparapu2014} to derive luminosity and planetary mass-dependent edges of the \gls{HZ} $a_\mathrm{inner}$ and $a_\mathrm{outer}$.
We further follow \citet{Bixel2021} and classify as \glspl{EEC} all planets with radii $0.8 S^{0.25} < R < 1.4 $ that orbit within the above boundaries.
The lower limit was suggested as a minimum planet size to retain an atmosphere~\citep{Zahnle2017}.

>>>>

\subsubsection{Simulated star and planet sample}
We generated two sets of synthetic exoplanet populations, one for FGK-type stars and one for M-type stars.
The stellar samples are drawn from the Gaia Catalogue of Nearby Stars~\citep{Smart2021} with a maximum Gaia magnitude of \var{M_G_max} and a maximum stellar mass of \var{M_st_max} \SI{}{\Msun}.
We included stars out to a maximum distance $d_{\max}$ that depends on the required planet sample size.
Planets were generated and assigned to the synthetic stars following the occurrence rates and size/orbit distributions of \citet{Bergsten2022}.
Following \citet{Bixel2021}, we considered only transiting \glspl{EEC} with radii $0.8\, S^{0.25} < R < 1.4 $ that are within the habitable zone (see Section~\ref{sec:met-hz}).
The lower limit was suggested as a minimum planet size to retain an atmosphere~\citep{Zahnle2017}.
To generate planet samples larger than what the stellar catalog in combination with these occurrence rates yields, we scaled up the occurrence rates by a constant factor that yields the desired number of planets.
This was in particular necessary for the FGK sample, where the rate of transiting planets that occupy the habitable zone is low.

For all survey simulations and hypothesis tests, we repeated the above in a Monte Carlo fashion to generate randomized ensembles of synthetic star and planet populations~\citep[compare][]{Bixel2021}.

\subsubsection{Habitable zone occupancy and UV flux}\label{sec:met-hz}
To test the UV hypothesis, we require that life occurs only on planets with sufficient past UV irradiation exceeding $F_\mathrm{NUV, min}$.
Further, we require this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.
All common Origin of Life scenarios require water as a solvent;
we thus consider only rocky planets that may sustain liquid water on their surface, i.e., that occupy their momentary \gls{HZ} during the above period.

Different formulations of habitable zones as regions around a star where a planet with Earth's atmospheric composition can maintain liquid water on its surface exist~\citep[e.g.,][]{MolLous2022,Spinelli2023,Tuchow2023}. CITE! Ramirez \& Kaltenegger 2017, 2018
Here, we adopt the popular estimates of \citet{Kasting1993} and \citet{Kopparapu2013,Kopparapu2014} that define a temperate zone between the runaway greenhouse transition CITE! and the maximum greenhouse limit CITE!.
We use the parametrization in \citet{Kopparapu2014} to derive luminosity and planetary mass-dependent edges of the \gls{HZ} $a_\mathrm{inner}$ and $a_\mathrm{outer}$.
